---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# hystReet
<!-- badges: start -->
[![CRAN](http://www.r-pkg.org/badges/version/hystReet)](https://CRAN.R-project.org/package=hystReet)
[![Downloads](https://cranlogs.r-pkg.org/badges/grand-total/hystReet)](https://www.r-pkg.org/pkg/hystReet)
[![R-CMD-check](https://github.com/JohannesFriedrich/hystReet/workflows/R-CMD-check/badge.svg)](https://github.com/JohannesFriedrich/hystReet/actions)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges: end -->


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "##",
                      fig.retina = 2,
                      fig.align = "center",
                      fig.path = "README_figs/README-")
Sys.setlocale("LC_TIME", "C")
```

## Introduction

[hystreet](https://hystreet.com) is a company that collects data on
pedestrian traffic in shopping streets of different European (mostly German) 
cities. After registering you can access and download the data via their website.


## Installation

The package is on CRAN. The easiest way to download is via:

```{r, eval=FALSE}
install.packages("hystReet")
```


You can install the development version from GitHub with the following command:

```{r, eval=FALSE}
if (!require("remotes"))
  install.packages("remotes")
remotes::install_github("JohannesFriedrich/hystReet")
```


```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(readr)
library(lubridate)
library(scales)
```


## API Keys

To use this package, you need to get a hystreet.com API key. To do so, you need to set up an account on [https://hystreet.com/](https://hystreet.com/). After that, you can find your personal API key
in the 'Profile' section of the webpage.

Now you have three options:

(1)
Once you have your key, you can save it as an environment variable for the current session by running the following command:

```{r, eval=FALSE}
Sys.setenv(HYSTREET_API_TOKEN = "PASTE YOUR API TOKEN HERE")
```


(2)
Alternatively, you can set it permanently with the help of `usethis::edit_r_environ()` by adding the following line to your `.Renviron`: 

```
HYSTREET_API_TOKEN = PASTE YOUR API TOKEN HERE
```

(3)
If you don't want to save your API token here, you can enter it for each function of this package using the `API_token` parameter.

## Usage

Function name       | Description                                        | Example
--------------------|----------------------------------------------------| -------
get_hystreet_stats() | request common statistics about the hystreet project | get_hystreet_stats() 
get_hystreet_locations() | request all available locations | get_hystreet_locations() 
get_hystreet_station_data() | request data from a stations  | get_hystreet_station_data(71)
set_hystreet_token() | set your API token | set_hystreet_token(123456789)

### Load some statistics

**Attention: The free API account does only provide access to one example location, which is Limburg.**

The function `get_hystreet_stats()` summarises the number of available stations and the sum of all counted pedestrians.

```{r}
library(hystReet)

stats <- get_hystreet_stats()
```

```{r, eval=FALSE}
stats
```

```{r echo=FALSE}
knitr::kable(stats, format = "html")
```


### Request all stations

The function `get_hystreet_locations()` generates a data frame with all available stations available to you as a user. 

```{r}
locations <- get_hystreet_locations()
```

```{r, eval = FALSE}
locations
```

### Request data from a specific station

The most useful function is `get_hystreet_station_data()`. Using the 'hystreetID' (the station's ID, 148 in the case of Limburg) it is possible to request data from a specific station. With the `query` argument it is necessary to define the time and sampling frame of the data: 

* `from`: datetime of earliest measurement (default: today 00:00:00:): e.g. "2021-10-01 12:00:00" or "2021-10-01"
* `to` : datetime of latest measurement (default: today 23:59:59): e.g. "2021-12-01 12:00:00" or "2021-12-01"
* `resolution`: Resolution for the measurement (default: hour): "day", "hour", "month", "week"

```{r, eval=FALSE}
data <- get_hystreet_station_data(hystreetId = 148,
                                  query = list(from = "2021-12-01", 
                                               to = "2021-12-31", 
                                               resolution = "day"))
```


## Some ideas for visualising the data

Let's see if we can find the busiest days in December 2024. Saturdays were probably quite busy, while there should have been substantially less pedestrian traffic on the 25th and 26th of December, both of which are holidays in Germany.

```{r}
data <- get_hystreet_station_data(hystreetId = 148, 
                                  query = list(from = "2024-12-01", 
                                               to = "2024-01-01", 
                                               resolution = "hour"))
```

```{r station_148}
ggplot(data$measurements, 
       aes(x = timestamp, 
           y = pedestrians_count, 
           colour = weekdays(timestamp))) +
  geom_path(group = 1) +
  scale_x_datetime(date_breaks = "7 days", 
                   labels = date_format("%d.%m.%Y")) +
  labs(x = "Date",
       y = "Pedestrians",
       colour = "Day",
       title = "Pedestrian counts for the example location of Limburg",
       subtitle = "Source: hystreet.com")
```

## Disclaimer
This package has been developed independently of and is not in any way associated to hystreet.com GmbH. 
Some parts of or calls to the API may exhibit unforeseen behaviour due to the API still being subject to changes. 
It is a simple wrapper providing R functions to access the hystreet.com API. 
The package authors are in no way responsible for the data that can be retrieved using its functions and do not provide 
support for any problems arising from the API’s functionality itself. Conversely, support for problems 
related to this package is exclusively provided by the package authors. 
The license of this package solely applies to its source code.